Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-16 intro.tex

\subsubsection{Parsing}
This parsing of date representations is one of the oldest data preparation problems we have observed. A common version of this problem is how to convert columns of integers of the form \texttt{yyyyMMdd} to date scalars. Na\"{i}ve users often solve this problem by converting the integer to a string and performing some locale-dependent string operations before casting the string back to a date. Unfortunately, this approach has a number of problems:
\begin{itemize}
\item String operations are notoriously slow compared to scalar operations (typically 10-100x slower in modern RDBMSes)
\item Default parsing of date formats is locale-dependent, and may not work when the analysis is shared across an international organization (\eg between the US and European offices)
\item The parsing code is hard to understand and maintain because it uses a verbose, general-purpose string-handling syntax instead of a specialized domain language.
\end{itemize}

>>>>

\subsubsection{Parsing}
This parsing of date representations is one of the oldest data preparation problems we have observed. A common version of this problem is how to convert columns of integers of the form \texttt{yyyyMMdd} to date scalars. Na\"{i}ve users often solve this problem by converting the integer to a string and performing some locale-dependent string operations before casting the string back to a date. Unfortunately, this approach has a number of problems:
\begin{itemize}
\item String operations are notoriously slow compared to scalar operations (typically 10-100x slower in modern RDBMSes)
\item The parsing code was hard to understand and maintain because it used a verbose, general-purpose string-handling syntax instead of a specialized domain language.
\item Default parsing of date formats is locale-dependent, and may not work when the analysis is shared across an international organization (\textit{e.g} between the US and European offices)
\item The parsing code is hard to understand and maintain because it uses a verbose, general-purpose string-handling syntax instead of a specialized domain language.
\end{itemize}
